Analysis PPM-S

### 2021-01-29 docs/prod_analysis-group_invariance.rmd

```{r tb_loads-fit-fac02}
fm01<- data.frame(t(data.frame(fitmeasures(fs1_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm01) ="M1.1"

#------chi2, df------#
fm04.1 <- fm01 %>% select(chisq.scaled,df) 
fm04.1$chisq.scaled <- round(x = fm04.1$chisq.scaled,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq.scaled,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")

#------CFI, RMSEA------#
fm04.2 <- fm01 %>% select(cfi.scaled,rmsea.scaled)
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

@@

#------ merge ------#
tb.fm2<- bind_rows(loads01,fm.df)
tb.fm2<- tb.fm2 %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4)
tb.foot <- paste0("Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures for the second sample"

>>>>

```{r tb_loads-fit-fac02}
fm01<- data.frame(t(data.frame(fitmeasures(fs1_o, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm01) ="M1.1"

#------chi2, df------#
fm04.1 <- fm01 %>% select(chisq,df) 
fm04.1$chisq <- round(x = fm04.1$chisq,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")

#------CFI, RMSEA------#
fm04.2 <- fm01 %>% select(cfi,tli,rmsea)
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

@@

#------ merge ------#
tb.fm2<- bind_rows(loads01,fm.df)
tb.fm2<- tb.fm2 %>% 
  mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{TLI}$","$\\text{RMSEA}$","$N$")) %>%
  select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4)
tb.foot <- paste0("Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures for the second sample"

### 2021-01-29 production/prod_analysis-cfa.rmd

corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
windowsFonts(A = windowsFont("Times New Roman"))
rownames(cor04$rho) <-c(
    "A. Perception Effort",
    "B. Perception Talent",
    "C. Perception Rich parents",
    "D. Perception Contacts",
    "E. Preferences Effort",
    "F. Preferences Talent",
    "G. Preferences Rich parents",
    "H. Preferences Contacts")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
save(cor04, file = "output/images/correlation.RData")
corrplot(
  cor04$rho,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A", 
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)

@@

corrplot(
  cor04$rho,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A", 
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)

@@

@@

#-------#
fm01<- data.frame(t(data.frame(fitmeasures(fit1_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm01) ="M1.1"
fm02<- data.frame(t(data.frame(fitmeasures(fit2_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm02) ="M2.1"
fm03<- data.frame(t(data.frame(fitmeasures(fit3_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm03) ="M3.1"

#------chi2, df------#
fm04<- round(rbind(fm01,fm02,fm03),3)
fm04.1 <- fm04 %>% select(chisq.scaled,df) 
fm04.1$chisq.scaled <- round(x = fm04.1$chisq.scaled,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq.scaled,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

#------CFI, RMSEA------#
fm04.2 <- fm04 %>% select(cfi.scaled,rmsea.scaled) 
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

@@

#------ merge ------#
tb.fm<- bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>% select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.foot <- paste0("; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
          column_spec(column = 2:13,width = "1cm",width_min = "1.3cm",include_thead = TRUE) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
save(tb.fm01,file = "output/tables/tb.fm01.RData")

>>>>

corrplot(cor01$rho,method = "color" ,type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

```{r}
cor04<-polychoric(select(dat04,perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw))
windowsFonts(A = windowsFont("Times New Roman"))
rownames(cor04$rho) <-c(
    "A. Perception Effort",
    "B. Perception Talent",
    "C. Perception Rich parents",
    "D. Perception Contacts",
    "E. Preferences Effort",
    "F. Preferences Talent",
    "G. Preferences Rich parents",
    "H. Preferences Contacts")
colnames(cor04$rho) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)", "(H)")
cor04$rho[cor04$rho==1] <- NA
save(cor04, file = "output/images/correlation.RData")
corrplot(
  cor04$rho,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A",
  na.label = "-",
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)

@@

corrplot(
  cor04$rho,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A", 
  na.label = "-",
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)

@@

```{r meas03-0, eval=FALSE, include=TRUE}
nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception contacts",
              "Preference effort","Preference talent","Preference rich family","Preference contacts",
              "Perception \n meritocratic","Perception \n non meritocratic","Preference \n meritocratic","Preference \n non meritocratic")

# graphics.off()
fm03<- data.frame(v1=fitmeasures(fit4_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),])
fm03 <- round(fm03,3)
par(mai = c(2,2,2,2)) # Set the margin on all sides to 2
par(mar = c(5, 5, 5, 5)) # Set the margin on all sides to 6
layout(matrix(c(1, # semPlot
                1, # semPlot
                1,
                1,
                1,
                2),# ajuste
              nrow=6,
              byrow=TRUE))

layout.show(n = 2)
semPaths(
  fit4_o ,
  # whatLabels = "std", # Indica si aparecen los valores
  what = "mod",
  label.cex = 1.3, # Tamaño de las etiquetas dentro de los nodos.
  edge.label.cex =  0.8, #  0.8 Tamaño de los valores estimados.
  residuals = T,
  optimizeLatRes =F,
  edge.color = "black",
  style = "lisrel",
  nCharNodes = 0,
  curvePivot = F,
  curve = 2.5,
  rotation = 4,
  layout = "tree2",
  cardinal = "lat cov",
  legend.cex = 0.6, # 0.6
  label.cex = 1,
  label.font = 6,
  edge.label.font = 14,
  asize = 3,
  edge.width = 1.2,
  sizeMan = 8,# largo manifest
  sizeMan2= 8,# alto manifest
  sizeLat = 5.5, # largo de los circulos
  sizeLat2 = 20, # alto de los circulos
  residScale = 10,
  width = 21.5, # 17
  height = 10, # 10
  # nodeNames = nodeNames,
  intercepts = F,
  reorder = T,
  thresholds = F,
  fixedStyle =1,
  node.height = 1,
  node.width = 4,
  label.scale = F,
  shapeMan = "rectangle",
  shapeLat = "ellipse",
  nodeLabels = nodeNames,
  details = T)

ld<- standardizedsolution(fit4_o) %>% select(lhs,op,rhs,est.std) %>% filter(op=="=~") 
ld$est.std<- sprintf("%.2f", ld$est.std)

#pegar cargas factoriales al plot
text(x = -0.1,y =  1.00, ld$est.std[1],font = 5,cex = 1.20)
text(x = -0.1,y =  0.85, ld$est.std[2],font = 5,cex = 1.20)
text(x = -0.1,y =  0.43, ld$est.std[3],font = 5,cex = 1.20)
text(x = -0.1,y =  0.26, ld$est.std[4],font = 5,cex = 1.20)
text(x = -0.1,y = -0.15, ld$est.std[5],font = 5,cex = 1.20)
text(x = -0.1,y = -0.30, ld$est.std[6],font = 5,cex = 1.20)
text(x = -0.1,y = -0.73, ld$est.std[7],font = 5,cex = 1.20)
text(x = -0.1,y = -0.88, ld$est.std[8],font = 5,cex = 1.20)

library(draw) #para hacer rectangulo de fit

adj_y <- 0.6
adj_x <- 0.2
drawBox(x = 3.5, y = 1.2-adj_y, width = 7.5, height = 2,fillColor = "grey",opacity = 0)# marca espacio
drawBox(x = 3.5, y = 1.4-adj_y, width = 5.5, height = 1,fillColor = "grey",opacity = 0.5) # crea rectangulo

# paste0("Estimator DWLS", ", N=",nobs(fit4_o))
# paste0("Model fit: ", "χ²","(",fm03[2,],")=",fm03[1,],"***","; CFI=",fm03[3,],"; RMSEA=",fm03[4,])
# paste0("***p<0.001")

#pegar texto fit en rectangulo

size <- 10

drawText(x = 1.4+adj_x, y = 1.75-adj_y, text = paste0("Estimator: DWLS", ", N=",nobs(fit4_o)),family = "serif",size = size)
drawText(x = 2.3+adj_x, y = 1.59-adj_y, text = paste0("Model fit: ", "χ²","(",fm03[2,],")=",fm03[1,],"***","; CFI=",fm03[3,],"; RMSEA=",fm03[4,]),family = "serif",size = size)
drawText(x = 1.0+adj_x, y = 1.43-adj_y, text = paste0("***p<0.001"),family = "serif",size = size)

#guardar en png
drawExport("output/images/meas03.png",units = "cm",width = 18,height = 15,ppi = 300) 
```

```{r lat-corr}
latcor<- lavInspect(fit4_o,what = "cor.lv")
windowsFonts(A = windowsFont("Times New Roman"))
rownames(latcor) <-c(
  "A. Meritocratic Perception",
  "B. Non-Meritocratic Perception",
  "C. Meritocratic Preferences",
  "D. Non-Meritocratic Preferences"
)
colnames(latcor) <-c("(A)", "(B)","(C)","(D)")
latcor[latcor==1] <- NA
png("output/images/latcor.png",
    width = 18,height = 13,units="cm",
    pointsize=12,bg="white",res=300)
corrplot(
  latcor,
  method = "color",
  type = "upper",
  tl.col = "black",
  addCoef.col = "black",
  diag = TRUE,
  family = "A",
  na.label = "-",
  number.font = 6,
  tl.cex =0.75,
  number.cex = 1)
dev.off()
```

@@

#-------#
fm01<- data.frame(t(data.frame(fitmeasures(fit1_o, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm01) ="M1.1"
fm02<- data.frame(t(data.frame(fitmeasures(fit2_o, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm02) ="M2.1"
fm03<- data.frame(t(data.frame(fitmeasures(fit3_o, output ="matrix")[c("chisq","df","cfi","tli","rmsea"),]))); row.names(fm03) ="M3.1"

#------chi2, df------#
fm04<- round(rbind(fm01,fm02,fm03),3)
fm04.1 <- fm04 %>% select(chisq,df) 
fm04.1$chisq <- round(x = fm04.1$chisq,digits = 1)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

#------CFI, RMSEA------#
fm04.2 <- fm04 %>% select(cfi,tli,rmsea) 
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

@@

#------ merge ------#
tb.fm<- bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{TLI}$","$\\text{RMSEA}$","$N$")) %>% select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.foot <- paste0("; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          # column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
          # column_spec(column = 2:13,width = "1cm",width_min = "1.3cm",include_thead = TRUE) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
save(tb.fm01,file = "output/tables/tb.fm01.RData")
